---
title: "Project"
output: pdf_document
geometry: margin=3cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**What is the research question you wish to explore? **
To propose/build a Ordinary Least Squares (OLS) regression model to
bring the possibility of a relation between the cancer mortality rates (dependent variable) and several potential socio-economic & geographical predictors.

**Introduction to the matter that you are examining.**



*****
**The motivation behind the chosen problem (you may cite some relevant
literature on the topic)**
While it may well be that disease incidence is rooted in biology, the mortality that ensues from that disease is a sociological phenomenon.
Disease maybe random, but death can be predicted.
This hypothesis underpins the attempts to 
link cancer mortality rates to socio-economic factors, rather than to biological/hereditary ones. 
The nature of socio-economic arrangements we set in place for ourselves, as a society, influences when & where an incidence might into mortality or not.
Disenfranchised regions/communities, characterized by State neglect in terms of resource allocation & redistribution and/or populated by historically 

*****
**Describe the data set you wish to explore. This includes describing the
observations in the data, a general description of the variables, and how the original curator of the data collected it)**
```{r}
cancer_df<-read.csv('cancer_reg.csv',sep = ",")
names(cancer_df)
```
Each row in the data set correspond to aggregated demographic data for one particular US county.
The data consists of 34 variables, 33 of which are continuous. 
And the one another, the 'geography' variable, a string consisting of the name of the county and the state in which it is located, is a unique categorical variable
and is the primary identifier/key for a given row.

the dependent variable which is the focus of the OLS regression is __'TARGET_deathRate'__ of a given county identified by the variable __'Geography'__.

__'TARGET_deathRate'__ is the mean per capita (100,000) lung cancer mortalities
over the period of 2010-2016

summary & sample of __'Geography'__ variable
```{r}
#head(cancer_df$Geography)
for (i in c(1,9,23)){
  print (cancer_df$Geography[i])
}
paste(c('no of samples/rows in dataset: ',dim(cancer_df)[1]), collapse="")
paste(c("no of unique 'Geography' variables: ",length(unique(cancer_df$Geography))), collapse="")

```
Four of the variables, together, describe the __racial makeup__ of the county 
as per 2013 census estimates. 

these include:

__'PctWhite'__:     % of county residents who identify as White

__'PctBlack'__:     % of county residents who identify as Black 

__'PctAsian'__:     % of county residents who identify as Asian

__'PctOtherRace'__: % of residents who identify in a category which is not                             White/Black/Asian



__.__

__Eight__ of the variables, together, describe the aggregate __educational & employment__ details of the county residents as per 2013 census estimates. 

these include:

__'PctNoHS18_24'__        : % of residents ages 18-24, with highest                                    education attained: less than high school 

__'PctHS18_24'__          : % of residents ages 18-24, with highest                                    education attained: high school diploma

__'PctSomeCol18_24'__     : % of residents ages 18-24, with highest                                    education attained: some college

__'PctBachDeg18_24'__     : % of residents ages 18-24, with highest                                    education attained: bachelor's degree

__'PctHS25_Over'__        : % of residents ages 25 & over, 
                            with highest education attained: high school diploma

__'PctBachDeg25_Over'__   : % of residents ages 25 & over, 
                            with highest education attained: bachelor's degree

__'PctEmployed16_Over'__  : % of residents ages 16 & over, employed

__'PctUnemployed16_Over'__: % of county residents ages 16 & over, unemployed

__.__

__Five__ of the variables, together, describe the aggregate __social security coverage__ details of the county residents as per 2013 census estimates.

__'PctPrivateCoverage'__: % of county residents with private health coverage

__'PctPrivateCoverageAlone'__: % of residents with private health coverage alone (no public assistance) 

__'PctEmpPrivCoverage'__: % of residents with employee-provided private health coverage

__'PctPublicCoverage'__: % of county residents with State-provided health coverage

__'PctPubliceCoverageAlone'__: % of residents with government-provided health coverage alone
__.__

__Three__ variables, together, are used to capture the aggregate __economic__ standing of the county residents as per 2013 census estimates.

__'medianIncome'__: Median income per county

__'povertyPercent'__: Percent of populace in poverty

__'binnedInc'__: Median income per capita, binned by decile

__.__

__Three__ variables, together, are used to capture the __social support__ makeup of the county residents as per 2013 census estimates.

__'PercentMarried'__: % of county residents who are married

__'PctMarriedHouseholds'__: % of married households

__'AvgHouseholdSize'__: Mean household size of county

__.__

__Four__ variables, describe the relevant __medical__ details concerning
incidence, mortality and testing rates, aggregated county wise, over the period of 2010-2016 

__'avgAnnCount'__: : Mean number of reported cases of cancer diagnosed annually

__'avgDeathsPerYear'__: Mean number of reported mortalities due to cancer

__'incidenceRate'__: Mean per-capita (100,000) cancer diagoses

__'studyPerCap'__: Per-capita number of cancer-related clinical trials per county

__.__

The remaining __Five__ variables, deal with aspects relating to population statistics, as sourced from 2013 census

__'BirthRate'__: Number of live births relative to number of women in county

__'popEst2015'__: Population of county (b)

__'MedianAge'__: Median age of county residents (b)

__'MedianAgeMale'__: Median age of male county residents (b)

__'MedianAgeFemale'__: Median age of female county residents












*****
**Provide a summary of the data frame (glimpse function) Mention the dimensions of your data, the number of observations, and the number of variables.**
```{r, echo=FALSE}
library(dplyr)
library(ggplot2)
#glimpse(cancer_df)
#paste(c('the dimensions of the data are: ',dim(cancer_df)), collapse=" ")
#paste(c('the data has: ',dim(cancer_df)[1], ' rows/samples/observations & ', dim(cancer_df)[2],' attributes/variables/features'), collapse="")
#head(cancer_df)
ggplot()+
  geom_histogram(mapping=aes(cancer_df$MedianAgeMale),binwidth=1,fill=alpha('#C3D7A4',0.5),color='white')+
  geom_histogram(mapping=aes(cancer_df$MedianAgeFemale),binwidth=1,fill=alpha("#F4EDCA",0.2),color='black')

```



```{r}
#summary(cancer_df)
names(cancer_df)
```
```{r}
j=1
for (i in cancer_df[23,]){
  #print(j)
  print (c(names(cancer_df)[j],i))
  j=j+1

}

```
```{r, echo=FALSE, fig.width = 5, fig.height=5}
ggplot(cancer_df)+geom_point(mapping=aes(PctMarriedHouseholds,PercentMarried))

```
