---
title: "Untitled"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
library(data.table)
library(skimr)
library(VIM)
library(GGally)
library(leaps)
library(tidyverse)
library(reshape2)
library(gclus)
library(ggpubr)
library(caret)
```
```{r}
cancer_df <- read.csv("cancer_reg.csv")
cancer_df <- cancer_df%>% mutate(Geography = as.factor(Geography), 
                                     binnedInc = as.factor(binnedInc))
cancer_df %>% skim()
```
missing data
```{r}
aggr(cancer_df)
```
-3 attributes, namely PctPrivateCoverageAlone, PctEmployed16_Over & 
PctSomeCol18_24 have missing data for some counties. Those variables are 
dropped, with justification being that the relatively high level of 
correlation observed between these and other ‘complete’ attributes will 
be sufficient to capture the variation that these variables might have 
produced in the output.

-the ‘binnedInc’ has been recast into a categorical variable, 
with 10 categories, each one corresponding to one decile.

-The variable 'AvgHouseholdSize' has around 61 entries/observations less 
than 0.1, which is an impossibility as the household size has to start at 1, 
suggesting some error in the process of data aggregation. It’s likely that 
these anomalous values might have to be multiplied by 100.

-The ‘MedianAge’ attribute has around entries for 30 counties listed with 
abnormally high (>300) values. These errors have been corrected using the 
average of MedianAgeMale & MedianAgeFemale values.


```{r}
cancer_df <- cancer_df %>% mutate(AvgHouseholdSize = ifelse(AvgHouseholdSize<0.1, AvgHouseholdSize*100, AvgHouseholdSize))
```
```{r}
cancer_df<- cancer_df %>% select(-PctPrivateCoverageAlone, -PctEmployed16_Over, -PctSomeCol18_24, -Geography, -binnedInc)
```

Clustered Correlation heatmap of the 29 numeric variables, after the above corrections/modifications, with the resulting correlation values rounded,
is displayed below :

```{r, fig.width = 18, fig.height=18}
library(ggcorrplot)
cormat <- cor(cancer_df %>% select(-Geography, -binnedInc))
ggcorrplot(cormat, hc.order = TRUE, outline.col = "white", tl.cex = 14, colors = c("#6D9EC1", "white", "#E46726"), lab=TRUE, digits=2)
```

```{r, echo=FALSE}
library(dplyr)
library(ggplot2)
ggplot()+
  geom_histogram(mapping=aes(cancer_df$MedianAgeMale),binwidth=1,fill=alpha('#C3D7A4',0.5),color='white')+
  geom_histogram(mapping=aes(cancer_df$MedianAgeFemale),binwidth=1,fill=alpha("#F4EDCA",0.2),color='black')
```


```{r, echo=FALSE}
ggplot(cancer_df)+geom_point(mapping=aes(PctMarriedHouseholds,PercentMarried), size=0.5, color='#D55E00')

```
```{r, echo=FALSE}
ggplot(cancer_df)+geom_point(mapping=aes(PctEmpPrivCoverage,PctPrivateCoverage), size=0.5, color='yellow4')

```
```{r, echo=FALSE}
ggplot(cancer_df)+geom_point(mapping=aes(PctPublicCoverageAlone,PctPublicCoverage), size=0.5, color='yellow4')

```
```{r}
ggplot(cancer_df)+geom_point(mapping=aes(log(popEst2015), log(avgAnnCount)), size=0.1, color='#009E73')
```
```{r}
ggplot(cancer_df)+geom_point(mapping=aes(log(popEst2015), log(avgDeathsPerYear)), size=0.1, color='#009E73')
```
```{r}
ggplot(cancer_df)+geom_point(mapping=aes(incidenceRate, TARGET_deathRate), size=0.1, color='#009E73')
```

```{r}
cancer_df_mod<- cancer_df %>% select(-MedianAgeMale, -MedianAgeFemale, -PctMarriedHouseholds, -PctEmpPrivCoverage, -avgAnnCount, -avgDeathsPerYear, -PctPublicCoverage)
```
```{r}
full_fit <- lm(TARGET_deathRate ~ ., data = cancer_df_mod)
summary(full_fit)
```
```{r}
birthy<-c("TARGET_deathRate",
"povertyPercent",
"medIncome",
"popEst2015",
"MedianAge",
"PctPublicCoverageAlone")

GGally::ggpairs(cancer_df[,birthy])
```

```{r}
ggplot(cancer_df)+geom_point(mapping=aes(medIncome, TARGET_deathRate), size=0.1, color='goldenrod3')
```
```{r}
best_subset <- regsubsets(TARGET_deathRate~., cancer_df_mod, nvmax = 15,  method = "backward")
best_subset_summary<- summary(best_subset)
```
```{r}
cpx=which.min(best_subset_summary$cp)
bicx=which.min(best_subset_summary$bic)
adjr2x=which.max(best_subset_summary$adjr2)
adjr2<-ggplot()+geom_point(aes(seq_along(best_subset_summary$adjr2),
                               best_subset_summary$adjr2))+
  xlab("Number of variables")+ylab("Adjusted R2")+
  geom_line(aes(seq_along(best_subset_summary$adjr2),best_subset_summary$adjr2),
            color='darkgoldenrod3')+
  geom_point(aes(x=adjr2x, y=best_subset_summary$adjr2[adjr2x]), color='coral2', 
             shape = 'x', size=8)
  
cp<-ggplot()+geom_line(aes(x=seq_along(best_subset_summary$cp),
                           y=best_subset_summary$cp), color='chartreuse4')+
  xlab("Number of variables")+ylab("Cp")+
  geom_point(aes(x=seq_along(best_subset_summary$cp),y=best_subset_summary$cp))+
  geom_point(aes(x=cpx, y=best_subset_summary$cp[cpx]), color='coral2', shape = 'x', size=8)

bic<-ggplot()+geom_line(aes(x=seq_along(best_subset_summary$bic),
                            y=best_subset_summary$bic), color='deepskyblue3')+
  xlab("Number of variables")+ylab("BIC")+
  geom_point(aes(x=seq_along(best_subset_summary$bic),y=best_subset_summary$bic))+
  geom_point(aes(x=bicx, y=best_subset_summary$bic[bicx]), color='coral2', 
             shape = 'x', size=8)
plotbest<-ggarrange(adjr2, cp, bic, ncol = 2, nrow = 2)
annotate_figure(plotbest, top = text_grob("Best Subset Selection, nvmax=20", 
               color = "darkslategrey", face = "bold", size = 15))
```
```{r}
plot(best_subset, scale = "bic")
```
```{r}
ggplot(cancer_df)+geom_point(mapping=aes(PctEmpPrivCoverage, TARGET_deathRate), size=0.1, color='dodgerblue3')
```
```{r}
ggplot(cancer_df) +geom_boxplot(aes(y=incidenceRate),width = 1)
boxplot(cancer_df$incidenceRate, data=cancer_df, boxwex=.9)
```